Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-27 manuscript/manuscript.Rmd
modifies forecast horizons to be from mean parameter runs, for now; adds plot to ms

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{./components/forecast_horizon.png}
  \caption{The forecast horizons for both models when used to forecast the final observation (cover in year 1945) starting from all possible prior years. For example, simulations initialized with cover in 1932 have 13 years before the forecast.}
\end{figure}
